Actuator line modeling of vertical-axis turbines

### 2016-08-27 reviews/reviewer1-response.md

As noted in the "Novelty" file, this work presents some results that have either never been simulated or reported before:

1. Validating with Reynolds numbers more representative of a full-scale turbine, and two orders of magnitude higher than those used by Shamsoddin and Porte-Agel.
2. Reporting performance predictions, which has also not yet been done for a VAT in an ALM simulation.
3. Embedding the ALM inside of a RANS model for additional computational affordability.

The reviewer is correct that we had not sufficiently described this novelty in
the paper itself, and we have updated the introduction accordingly.

>- Minor comment: I'd rather use nondimentional units for variables such as time step

Figure 6 does use a time step that is technically nondimensional (time steps per rotor revolution).

>Pages 1-6: Again, very good introduction and gathering of introductory note,
but in my opinion, it should be shortened for a journal.

We agree and have shortened the introduction significantly.

TODO: Shorten introduction

>Page 7, Fig 3: It is taking a lot of room, perhaps you can make a smaller
schematic

We have made this figure smaller in the manuscript, a change that may be
retained by the typesetter.

>Page 9 fig 6: The Cp figure is an interesting one. But first of all, but is
there a particular reason why you have not shown Ct next to it (it's more common
this way than having Cd). Also, would it not be possible to have LES results on
top of both figures 6 and 11 for the cases you have simulated?

We use the overal rotor drag coefficient nomenclature ($C_D$) since this was
adopted by Paraschivoiu (2001). As noted, this is commonly called the thrust
coefficient for horizontal-axis turbines. We have added a note to the manuscript
to clarify this.

We have not plotted the LES results, since we only used LES for one tip speed
ratio, and for one turbine---it was mainly employed to assess wake predictions.

>Page 11, Line 42: I'm not quite sure if what you have stated about Smagorinsky
model is correct. It certainly is very easy to implement and gives nice results
in some cases, but we are all aware of its deficiencies. We set a fix Cs value
which means we add numerical dissipation to the whole computatiponal domain, but
this is not really accurate when dealing with cases with strong directional
homogeneity and anisotropy. Why didn't you choose a dynamic Smagorinsky or even
dynamic Lagrangian model? Besides, what is the Cs value you have used?

Firstly, the $C_S$ value used was OpenFOAM's default value of approximately
0.17. This detail has been added to the text.

Secondly, we are not trying to claim that the Smagorinsky model is the most
accurate "standard" model, but that is has been used in many other ALM papers,
and therefore a good baseline for comparison. The wording of the text has been
adjusted to reflect the notion that we are interested in this comparison to
baseline for turbine ALM modeling.

>Page 13, Fig 15: Following my last comment, figure to the right may very well explain that the
Smagorinsly model has been over dissipative thereby hampering turbulent fluctuations which may have otherwise resulted in higher TKEs.
>
Page 14, Line 27: Matching mean velocities is usually rather straightforward (in non-presudospectral
codes, sometimes even shutting down the whole SGS modeling wouln'd make a difference as long as no solid walls are involved). But higher order moments such as Reynolds stress tensor components are usually more sensitive. Perhaps you can go more in depth with that part -- possibly compare your
results with other experiments or CFD simulations. Besides, please try and overcome the relatively large discrepancies seen in figures 6 (high TSR), 9, 11.

### 2016-08-27 paper.tex
Note how the Smagorinsky model is a good baseline, not necessarily the most accurate SGS model

Thus, the UNH-RVAT baseline case was simulated using the Smagorinsky LES
turbulence model \cite{Smagorinsky1963}, which was the first of its kind, and
serves as a good standard for LES modeling since its behavior is well-reported
in the literature. OpenFOAM's default Smagorinsky model coefficients were used
(giving an approximate equivalent Smagorinsky coefficient $C_S = 0.17$), and the
LES filter width was set as the cube root of the local cell volume. The tip
speed ratio was set to oscillate sinusoidally about $\lambda_0$ with a 0.19
magnitude and the angle of the first peak at 1.4 radians---similar to the
rotation presribed in the blade-resolved RANS simulations discussed in
\cite{Bachant2016-BR-CFD}.

>>>>

Thus, the UNH-RVAT baseline case was simulated using the Smagorinsky LES
turbulence model \cite{Smagorinsky1963}, which was the first of its kind, and
serves as a good baseline for LES modeling since its behavior is well-reported
in the literature, especially for ALM simulations. OpenFOAM's default
Smagorinsky model coefficients were used (giving an approximate equivalent
Smagorinsky coefficient $C_S = 0.17$), and the LES filter width was set as the
cube root of the local cell volume. The tip speed ratio was set to oscillate
sinusoidally about $\lambda_0$ with a 0.19 magnitude and the angle of the first
peak at 1.4 radians---similar to the rotation presribed in the blade-resolved
RANS simulations discussed in \cite{Bachant2016-BR-CFD}.
